Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-21 paper/main.tex
rewrite short subsection on numerical implementation

% --------------------------------------------------------------------------------------------------
\subsection{Numerical Implementation}
We implemented the described model in our recently developed \ac{abm} framework
\texttt{cellular\_raza}~\cite{Pleyer2025}.
By design \texttt{cellular\_raza} does not assume any particular cellular representation, thus makes
it flexible and easy to adapt the simulation to particular needs.
Its design allows us to experiment with different model implementations while retaining fast
execution times.
\textbf{[Der Zusammenhang zwischen der Flexibilität und Performance ist unklar.]}
\textit{Oft muss man das eine für das andere opfern. Hier nicht/kaum.}

Furthermore, it is an \ac{abm} which is able to natively track cells through the course of a
numerical simulation and also keeps track of mother/daughter relationships.
\textbf{[Das scheint hier trivial zu sein.]}
\textit{Machen aber viele (zB. PhysiCell) einfach nicht. (Mother-Daughter relation)}

>>>>

% --------------------------------------------------------------------------------------------------
\subsection{Numerical Implementation}
We implemented the described model in our recently developed \ac{abm} framework
\texttt{cellular\_raza}~\cite{Pleyer2025}.
By design \texttt{cellular\_raza} does not assume any particular cellular representation, which
makes it flexible and easy to adapt the simulation to particular needs.
Its design allows us to experiment with different model implementations and facilitates the
explorative capabilities of researchers.
It is furthermore able to seamlessly integrate into Python code-bases thus allowing us to utilize
methods from other popular software libraries such as \texttt{numpy} and \texttt{scipy}.
Furthermore, it is an \ac{abm} which is able to natively track mother-daughter relations of cells
over the course of a numerical simulation which is an integral component of our imaging-based
comparison algorithm (see section~\ref{subsec:imaging-based-comparison}).
